A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-08 paper.tex
Hardware acceleration with referrence

The E2EE protocol presented in this paper combines a series of different cryptographic procedures. Each of them can be chosen according to the working hardware and scenario. On some hardwares, the developers can choose the cryptographic methods with hardware acceleration. With hardware acceleration, the elapsed time could be dropped a step more.

>>>>

\begin{figure}[!t]
    \centering
    \includegraphics[width=2.5in]{AES-NI}
    \caption{AES256 Encryption/Decryption Performance Numbers}
    \label{fig:AES-NI}
\end{figure}

The E2EE protocol presented in this paper combines a series of different cryptographic procedures. Each of them can be chosen on the basis of the working hardware and scenario by developers. On some certain devices, hardware acceleration would be supported. With hardware acceleration, the elapsed time could be dropped a step more. For example applying AES-NI can accelerate AES operations around 40\% on Intel devices.\cite{AES-NI-Acceleration} Fig.~\ref{fig:AES-NI} shows the performance of Encryption/Decryption of AES256 with and without hardware acceleration.
